Impact of Satellite Constellations on the Legacy Survey of Space and Time

### 2022-10-06 ms.tex

\end{abstract}

@@

XXX--I'll add some text describing the baseline scheduler that we use--note that we only run for the first year. Maybe add a zonodo to the repo so we can cite where we got the baseline simulation from.

@@

\begin{figure}[ht!]
\plottwo{plots/streaklen_v_weight.pdf}{plots/streakfrac_v_weight.pdf}
\plottwo{plots/nexp_v_weight.pdf}{plots/deltam_v_weight.pdf}
\caption{Results from simulating the first year of Rubin observations in the presence of different satellite constellations and varying how strongly the scheduler attempts to avoid satellites.  Top panels show that, as expected, the number of streaks and mean streak length decrease as more emphasis is put on satellite dodging. Bottom panels show the resulting trade off, as avoiding satellites forces the scheduler to make longer slews and observe less desirable parts of the sky, resulting in fewer total exposures in the first year and a shallower median coadded depth in $g$.
xxx--could stack these and share the x-axis. Need to fix the y-label getting cut off.
\label{fig-pixel-loss-weight}}
\end{figure}

@@

\begin{figure}
    \centering
    \plottwo{plots/temp}{}
    \caption{Caption}
    \label{fig:twi_neo}
\end{figure}

@@

>>>>

XXX--bottom line. Even in the case of multiple mega constellations in orbit, we expect Rubin would only lose $\sim$0.02\% of science pixels to streaks. Given reasonable satellite orbit predictions we find we can reduce pixel losses by a factor of 2 with minimal impact to the survey science goals. Even so, the tiny fraction of pixels lost makes mitigation strategies unnecessary. Twilight observations at high airmass with no scheduling mitigation could see pixel losses up to 0.06\%. 
\end{abstract}

@@

XXX--I'll add some text describing the baseline scheduler that we use--note that we only run for the first year. As a starting point we use the baseline scheduler simulation in \citet{yoachim2022}.

@@

\begin{figure}[ht!]
\plottwo{plots/streaklen_v_weight.pdf}{plots/streakfrac_v_weight.pdf}
\plottwo{plots/nexp_v_weight.pdf}{plots/deltam_v_weight.pdf}
\caption{Results from simulating the first year of Rubin observations in the presence of different satellite constellations and varying how strongly the scheduler attempts to avoid satellites.  Top panels show that, as expected, the number of streaks and mean streak length decrease as more emphasis is put on satellite dodging. Bottom panels show the resulting trade off, as avoiding satellites forces the scheduler to make longer slews and observe less desirable parts of the sky, resulting in fewer total exposures in the first year and a shallower median coadded depth in $g$.
xxx--could stack these and share the x-axis. 
\label{fig-pixel-loss-weight}}
\end{figure}

@@

\begin{figure}
    \centering
    \plottwo{plots/temp/opsim_Count_night_night_lt_366_and_visitExposureTime_lt_20_HEAL_SkyMap.pdf}{plots/twilight_curves.pdf}
    \caption{Impact of streaks on twilight NEO observations that can not easily be shifted to dodge satellites. Left panel shows the altitude, azimuth distribution of NEO observations in a recent survey simulation. The right panel shows the number of streaks that would result from different satellite constellations as a function of observation altitude. The legend includes an estimate of the pixel loss percentage for NEO observations assuming a 50 pixel wide mask is used. }
    \label{fig:twi_neo}
\end{figure}

@@

We find larger constellations will only leave streaks on $\sim10$\% of Rubin images. This is a much lower value than previous studies \citep{lawrence22, tyson20}. This is partly due to the latest Starlink plans not including higher altitude orbits that were included in the \citet{tyson} study. % And partly due to not conflating twilight observations with the whole survey.

XXX--While satellite streaks are poised to be a nuisance to Rubin observations, it is important to remember 1) They do not saturate detectors, 2) Do not leave streaks when in earth's shadow, 3)
